Phenotypic evolution is less constrained in complex food webs or Food-web complexity alters the fitness landscape of an insect herbivore

### 2018-09-20 ms_complexity_selection.Rmd
updated coefficient estimates from full model. Need to revise so that coefficients that are not influenced by food web do not receive separate estimates.

@@

# There is also clear evidence that our food-web treatment altered natural selection
anova(trait_glmer, foodweb_glmer)
rsquared(list(trait_glmer, foodweb_glmer), method="delta") # 3-4% increase in amount of variance explained when including effect of food-web treatment

@@

# There are no clear patterns in the distribution of the residuals (= good)
visreg(foodweb_glmer)

# Overall, there is clear evidence that food-web treatment alters absolute fitness
anova(null_glmer, trait_glmer, foodweb_glmer, test = "Chisq") 
```

```{r REVISED Get Selection Gradients for GLMER}

@@

# test whether using alternative models influences estimes of mean "brackets" and mean fitness 
alt_predict <- predict(foodweb_glmer_beta, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
alt_mean_brackets <- mean(alt_predict * (1 - alt_predict))
alt_mean_fitness <- mean(alt_predict)
complex_mean_brackets - alt_mean_brackets
complex_mean_fitness - alt_mean_fitness

# Altering so that coefficients that differed between food webs are reported, but ones that weren't are simply reported as there baselines.
# Added multiplier column so that quadratic (nonlinear) selection coefficients can be multiplied by 2 for fair comparison
foodweb_tidy_betas <- tidy(foodweb_glmer_beta, conf.int=T) %>%
  filter(term %in% c("(Intercept)","FoodwebSimple","sc.Diam","sc.log.Clutch","sc.log1p.Pref",
                     "FoodwebSimple:sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.log1p.Pref")) %>%
  mutate(Foodweb = c("Complex","Simple",rep("Complex",3),rep("Simple",3)),
         Selection_form = c(NA,NA,rep("Directional",6)),
         Multiplier = rep(1,8))

foodweb_tidy_gammas <- tidy(foodweb_glmer, conf.int=T) %>%
  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)",
                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref",
                     "FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.log1p.Pref^2)",
                     "FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.log1p.Pref","FoodwebSimple:sc.log.Clutch:sc.log1p.Pref")) %>%
  mutate(Foodweb = c(rep("Complex",6),rep("Simple",6)),
         Selection_form = c(rep("Nonlinear",3),rep("Correlational",3),rep("Nonlinear",3),rep("Correlational",3)),
         Multiplier = c(rep(2,3),rep(1,3),rep(2,3),rep(1,3)))

get_alphas <- bind_rows(foodweb_tidy_betas, foodweb_tidy_gammas) %>% 
  mutate(alpha = estimate, alpha_2.5 = conf.low, alpha_97.5 = conf.high, P = p.value) %>%
  select(term, Foodweb, alpha, alpha_2.5, alpha_97.5, P, Selection_form, Multiplier)

@@

We found that changes in food-web complexity fundamentally altered the shape of *Iteomyia*'s fitness landscape (statistical test for trait vs. food-web*traits).

>>>>

# Model excluding quadratic and trait:trait interactions. This is necessary for accurately estimating directional selection gradients (Betas, Lande and Arnold 1983)
betas_glmer <- glmer(gall_survival ~ Foodweb*(sc.Diam + sc.log.Clutch + sc.log1p.Pref) +
                         (1|Genotype/Plant_Position/Gall_Number),
                       data = gall_selection.df,
                       family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))

@@

# There is also clear evidence that our food-web treatment altered natural selection
foodweb_test <- tidy(anova(trait_glmer, foodweb_glmer, test="Chisq"))
rsquared(list(trait_glmer, foodweb_glmer), method="delta") # 3-4% increase in amount of variance explained when including effect of food-web treatment

@@

# There are no clear patterns in the distribution of the residuals (= good)
visreg(foodweb_glmer)
```

## METHOD OF JANZEN AND STERN 1998 ----

# Estimate mean fitness and mean "brackets" for each food-web treatment (see Janzen and Stern 1998 equation 4 for details about "brackets")
complex_predict <- predict(foodweb_glmer, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
complex_mean_brackets <- mean(complex_predict * (1 - complex_predict))
complex_mean_fitness <- mean(complex_predict)

@@

# Double-check that using the Beta-only model doesn't influence estimes of mean "brackets" and mean fitness. Using Complex food web as an example, but it doesn't matter 
alt_predict <- predict(betas_glmer, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
alt_mean_brackets <- mean(alt_predict * (1 - alt_predict))
alt_mean_fitness <- mean(alt_predict)
test_mean_brackets <- complex_mean_brackets
test_mean_fitness <- complex_mean_fitness
test_mean_brackets - alt_mean_brackets # virtually the same
test_mean_fitness - alt_mean_fitness # virtually the same

# Tidy data for beta terms
foodweb_tidy_betas <- tidy(betas_glmer, conf.int=T) %>%
  filter(term %in% c("(Intercept)","FoodwebSimple","sc.Diam","sc.log.Clutch","sc.log1p.Pref",
                     "FoodwebSimple:sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.log1p.Pref")) %>%
  mutate(Foodweb = c("Complex","Simple",rep("Complex",3),rep("Simple",3)),
         Selection_form = c(NA,NA,rep("Directional",6)),
         Multiplier = rep(1,8))

# Tidy data for gamma terms. Note that we multiply quadratic (nonlinear) selection coefficients by 2 so they are on the same scale as other coefficients (detailed explanation in Stinchcombe et al. 2008)
foodweb_tidy_gammas <- tidy(foodweb_glmer, conf.int=T) %>%
  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)",
                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref",
                     "FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.log1p.Pref^2)",
                     "FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.log1p.Pref","FoodwebSimple:sc.log.Clutch:sc.log1p.Pref")) %>%
  mutate(Foodweb = c(rep("Complex",6),rep("Simple",6)),
         Selection_form = c(rep("Nonlinear",3),rep("Correlational",3),rep("Nonlinear",3),rep("Correlational",3)),
         Multiplier = c(rep(2,3),rep(1,3),rep(2,3),rep(1,3)))

# Combine and tidy the regression (alpha) coefficients
get_alphas <- bind_rows(foodweb_tidy_betas, foodweb_tidy_gammas) %>% 
  mutate(alpha = estimate, alpha_2.5 = conf.low, alpha_97.5 = conf.high, P = p.value) %>%
  select(term, Foodweb, alpha, alpha_2.5, alpha_97.5, P, Selection_form, Multiplier)

@@

We found that changes in food-web complexity altered the shape of *Iteomyia*'s fitness landscape ($\chi^2_{`r foodweb_test$[2,"Chi.Df"]`}=`r foodweb_test$[2,"statistic"]`, P=`r foodweb_test$[2,"p.value"]`$).
